Manual evaluation of the results of Experiment III (index number is the row number in the csv file):

\begin{enumerate}
    \item 09GK, score 2: OK. \\
    Formal proof is one line using existing packages, while informal proof proves in detail. 
    \item 01Z2, score 4: OK\\
    Semantically the same, structurally, only one step has a different proof (Lean more general category theoretical)
    \item 01Z3, score 3:  OK\\
    semantically same, structurally the key intermediate proofs are different, as Lean uses a general category theory package
    \item 01Z4, score 2: NOT OK, perhaps should be 1\\
    Different proosf content with a little overlap, different structures
    \item 01Z4, score 2: OK\\
    Neither the same statement, not similar proof semantics, nor the same proof structure
    \item 01ZC, score2: OK\\
    Informal proof is an equivalence of three statements, while Lean proves only one part of the one of the statements via existing packages.
    \item 01Z5, score 4: OK\\
    Lean uses packages to prove the main statement, while informal proof details things and contains more steps.
    \item 01Z6, score 2: OK\\
    semantically goals have overlap, though not exactly the same. Proof structures/steps are irrelevant.
    \item 01OX, score 4: OK\\
    Same semantics and structure. Same steps except one that Lean uses packages
    \item 01OY, score 4:  OK\\
    Same semantics and structur of proof, though one step has differnt proof.\\
    \item 01OZ, score 4: OK\\
    Same semantical and structural proof. Proof of One step looks different: Lean uses a package, informally a lemma is used to prove the step
    \item 01P0, score 4: OK\\
    Same semantical and structural proof. Proof of One step looks different: Lean uses a package, informally a lemma is used to prove the step
    \item 0BA8, score 2:  OK\\
    Prove the same thing, the core argument is the same, but Lean and informal proofs differ structurally.
    \item 03GP, score 2, Perhaps better 1\\
    Not the same statement, not the same proof.
    \item 0AXN, score 4: OK\\
    Same statement, different proof, as each formal/informal uses different lemma
    \item 01QF, score 4: OK\\
    Same proof semantics and structure, except that one step is proved using different Package/Lemma
    \item 054K, score 5: Perhaps 4?\\
    Same proof steps, one step proofs slightly differs, as Lean proves in two statements while informally proved by a lemma.
    \item 04XU, score 1; OK\\
    entirely different proof structures
    \item 01U1, score 5: OK\\
    Same proof structure. One tiny difference in one step: Lean uses a package that is a more general result than informally used/required sentence.\\
    \item 0BN4, score 2: OK\\
    Lean only one final part of formal proof
    \item 002O, score 2: OK\\
    Lean is one statement out of several equivalences
\end{enumerate}
